Draft_Application_Stochastic_Volatility

### 2021-07-19 Real Dataset SV.Rmd
commit

>>>>

```{r include=FALSE}
Errorcomp<-matrix(NA,ncol=6,nrow=10)
colnames(Errorcomp)<-c("N","BPF", "GPFOPT", "APF", "SIS", "BAPF")
rownames(Errorcomp)<-c("RMSE","MAE","RMSE","MAE","RMSE","MAE","RMSE","MAE","RMSE","MAE")
Errorcomp[,1]<-c(10,10,100,100,1000,1000,5000,5000,10000,10000)
Errorcomp[,2]<-c(0.3780316,0.2581917,0.13740936,0.08692049,0.06682471,0.03859926,0.02801391,0.01508258,0.04292242,0.01831794)
Errorcomp[,3]<-c(0.3888922,0.2655844,0.13385416,0.08092348,0.05924883,0.03055189,0.05669256,0.02719531,0.04300498,0.02021422)
Errorcomp[,4]<-c(0.4952102,0.3869999,0.228981,0.1717977,0.10257034,0.07240061,0.04911414,0.02690089,0.0280415,0.01949516)
Errorcomp[,5]<-c(0.4601913,0.3651146,0.2447648,0.1838898,0.10985867,0.06507043,0.06133971,0.02966254,0.03314042,0.01913677)
Errorcomp[,6]<-c(0.9103835,0.7211173,1.101557,0.914675,0.6150409,0.4895908,0.6117618,0.4419522,0.5054665,0.4022079)

```

```{r echo=FALSE, message=FALSE, warning=FALSE, results="asis"}
library(kableExtra)
kbl(Errorcomp[,], align="c", longtable = T, booktabs = T, caption="RMSE and MAE, Auxiliary PF 50000 particles",digits=5)
```
